---
title: "Extracting lat-long for Distribution centers"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

This walks through how to extract lat-long data for distribution centers using the `ggmap` package. 

```{r}
library(ggmap)
library(readr)
library(fields)
```

Next we need to import the Greensboro Charlotte dataset.

```{r}
dc_data <- readr::read_csv('data/Greensboro Charlotte.csv')
```

Now, we need to paste the address for each location, which is stored in several columns of our data. The following code does this by creating an object called `address`.

```{r}
address <- paste(dc_data$`Customer Name`,
                 dc_data$City,
                 dc_data$State,
                 dc_data$`Postal Code`,
                 sep = ' ')
```


```{r}
Dimnames <- list(NULL, c('lon','lat'))
latlon2000 <- matrix(NA, nrow = 2000, ncol = 2, dimnames = Dimnames)
latlon4000 <- matrix(NA, nrow = 2000, ncol = 2, dimnames = Dimnames)
latlonrest <- matrix(NA, nrow = (length(address) - 4000), ncol = 2, dimnames = Dimnames)
```

Finally, we use the function `geocode` from the `ggmap` package to return the lat-lon data for each address.

```{r}
latlon2000 <- ggmap::geocode(address[1:2000])
save(latlon2000, file = 'data/latlon2000.RData')
```


Need to finish the rest later

```{r, eval=FALSE}
latlon4000 <- ggmap::geocode(address[2001:4000])
latlonrest <- ggmap::geocode(address[4001:length(address)])
```


```{r}
latlon <- as.data.frame(rbind(latlon2000, latlon4000, latlonrest))
```

Now, let's combine these results into a data.frame.

```{r}
df <- data.frame(Address = address,
                 longitude = latlon$lon,
                 latitude = latlon$lat)
```
save(latlon2000, file = 'data/latlon2000.RData')
> View(latlon2000.RData)
Error in View : object 'latlon2000.RData' not found
> load("C:/Users/Daria/github/DC-optimization/data/latlon2000.RData")
> View(latlon2000.RData)
 load("C:/Users/Daria/github/DC-optimization/data/latlon2000.RData")
> which(dc_data$City=='RUTHERFORDTON')

```{r}
dc1 <- geocode('201 Creek Ridge Rd Greensboro, NC 27406', source = 'dsk')

dist_from_dc <- fields::rdist.earth.vec(as.matrix(latlon2000dsk), 
                                        as.matrix(dc1))
```